Handling Recursion in Generic Programming Using Closed Type Families

### 2018-05-10 lncs-paper.tex
wibble

The location structure consists of the focal subtree, which is one of the mutually recursive nodes of total structure of the family of datatypes, and its surrounding context. We give the following definition of the datatype \texttt{Loc} for locations:
\texttt{
\vs
\indent data Loc (r \ann *) (fam \ann [*]) (c \ann * \ra Constraint) where\\
\indent\s\s Loc \ann\hs Family r a fam c \ra Contexts r a fam c\\
\indent\ind\s\s\ra Loc r fam c
\vs
}
The subtree in focus is wrapped by the \texttt{Family} datatype that we use to prove its required properties, while we do not know the current type of the node in focus. For being able to move up in the tree, we keep the type that will be obtained by uniting the current focus and context (essentially, the type of the focal node's parent in the tree): that type is unknown outside the location, and is reflected in the type parameters of \texttt{Family} and the \texttt{Contexts} datatype of the context by the type variable \texttt{a} that is existential in the \texttt{Loc} datatype; the type of the focal subtree itself is existential in \texttt{Family}. The other type parameters \texttt{r}, \texttt{fam}, and \texttt{c} in \texttt{Loc} mean the root type of the tree, the list of types constituting the family, and the constraint constructor imposing restrictions on the family's types, respectively.

>>>>

The location structure consists of a focal subtree, which is one of the mutually recursive nodes of the whole structure of the family of datatypes, and its surrounding context:
\texttt{
\vs
\indent data Loc (r \ann *) (fam \ann [*]) (c \ann * \ra Constraint) where\\
\indent\s\s Loc \ann\hs Family r a fam c \ra Contexts r a fam c\\
\indent\ind\s\s\ra Loc r fam c
\vs
}
The subtree in focus is wrapped by the \texttt{Family} datatype that we use to prove its required properties, while we do not know the current type of the node in focus. For being able to move up in the tree, we keep the type that will be obtained by uniting the current focus and context (essentially, the type of the focal node's parent in the tree): that type is unknown outside the location, and is reflected in the type parameters of \texttt{Family} and the \texttt{Contexts} datatype of the context by the type variable \texttt{a} that is existential in the \texttt{Loc} datatype; the type of the focal subtree itself is existential in \texttt{Family}. The other type parameters \texttt{r}, \texttt{fam}, and \texttt{c} in \texttt{Loc} mean the root type of the tree, the list of types constituting the family, and the constraint constructor imposing restrictions on the family's types, respectively.
